### 2014-11-13 locks.tex
small edits

As can be seen in Table~\ref{queue_instructions} all the coordinated
versions of the programs require significantly more queue operations.
The data for this table comes from recording the number of \emph{queue
operations} and facts derived.
Queue instructions represent the
number of normal queue operations executed (each costs 1) plus the
number of \emph{percolate-up}/\emph{percolate-down} operations
executed for each manipulation of the priority queue.  As expected,
programs which rely on prioritizing the order of execution to obtain
better asymptotic complexity (e.g., SSSP) improve in overall running
time at the cost of more queue operations.  In all cases, coordination
adds a significant number of total queue operations, but the resulting
overhead is more than compensated for by an improved schedule and reduction
in number of facts produced. For MiniMax and N Queens, the number of facts derived
is the same for all configurations, as expected. The performance seen for those programs
arise from reduced memory usage and improved memory locality.

@@

We next investigate the effect of coordination on the synchronization
overhead that comes from the use of more locks.  We measured the
\emph{basic locks}, the number of locks acquired
in the original LM virtual machine and \emph{coordination locks}, the
number of locks acquired to perform coordination operations.  We also
measured how often \mytt{lock()} operations that fail to acquired
the lock on the first attempt.  Lock failures happen so infrequently
(less than 1\% of the time) that they cannot be seen on the figures.

>>>>

As can be seen in Table~\ref{queue_instructions} all the coordinated
versions of the programs require significantly more queue operations.
The data for this table comes from recording the number of queue
operations and facts derived.  Queue operations represent the number
of normal queue operations executed (each costs 1) plus the number of
\emph{percolate-up}/\emph{percolate-down} operations executed for each
manipulation of the priority queue.  As expected, programs which rely
on prioritizing the order of execution to obtain better asymptotic
complexity (e.g., SSSP) improve in overall running time at the cost of
more queue operations.  In all cases, coordination adds a significant
number of total queue operations, but the resulting overhead is more
than compensated for by an improved schedule and reduction in number
of facts produced. For MiniMax and N Queens, the number of facts
derived is the same for all configurations, as expected. The
performance seen for those programs arise from reduced memory usage
and improved memory locality.

@@

We next investigate the effect of coordination on the synchronization
overhead that comes from the use of more locks.  We measured the
\emph{basic locks}, the number of locks acquired
in the original LM virtual machine and \emph{coordination locks}, the
number of locks acquired to perform coordination operations.  We also
measured how often \mytt{lock()} operations fail to acquire
the lock on the first attempt.  Lock failures happen so infrequently
(less than 1\% of the time) that they cannot be seen on the figures.
